VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-30 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
worked in suggestions from CMJ

\noindent
The notation $(\cdot)^{-1}$ denotes the functional inverse. The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively. Furthermore,
\begin{equation}
\label{eq:h_def}
h(x) = g^{-1}(x). 
\end{equation}
and
\begin{equation}
\label{eq:g_def}
g(x) = x - a\circ f(x) + a 
\end{equation}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{fig13.pdf}
\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$. The figure also depicts the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ as used in the Cavalieri sum (see equation~\eqref{eq:cav_sum}). Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
\label{fig:caval2}
\end{figure}

@@

\noindent
Let us express this idea more formally. Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$. Furthermore, consider the following lower Cavalieri sum (see Definition~\ref{def:cav_integral} and equation~\ref{eq:c_low}):
\begin{equation}
\label{eq:cav_sum}
\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in the left panel of Figure~\ref{fig:caval2} (if $n$ is set to 3). Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$. Equation~\eqref{eq:cav_sum}, therefore, approximates the area of $R$. In the limit equation~\eqref{eq:cav_sum} approaches 
the Cavalieri integral (see Definition~\ref{def:cav_integral}):
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
If we evaluate the above integral we obtain the area of $R$. It is, however, quite hard to evaluate the above integral in its present form. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
integral by using the functions $h$ and $g$ (see equation~\eqref{eq:g_def} and equation~\eqref{eq:h_def}). Expressed mathematically (see Theorem~\ref{t:conv}):
\begin{equation}
\label{eq:main_cav}
\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x),
\end{equation}
We can, therefore, evaluate equation~\eqref{eq:main_cav} in one of two ways:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75,  
\end{equation}
or
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
\end{equation}
Note: $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.\\

@@

\noindent
The natural question now arises, can we convert a Riemann-Stieltjes integral into a Cavalieri integral? As an example, can the following Riemann-Stieltjes integral be converted into a Cavalieri integral?
\begin{equation}
\int_{a'}^{b'} \,d\,\widetilde{g}(x) = \int_{\frac{1}{2}}^2 x\,d[2x+1].
\end{equation}
To accomplish this task we first need to compute the following (see Section~\ref{sec:cav_integral}):
\begin{itemize}
 \item $a(y) = f^{-1}(y) - \widetilde{g}\circ f^{-1}(y)+ \widetilde{g}(a') = 1-y$.
 \item $a = a(0) = 1$.
 \item $C = a - \widetilde{g}(a') = -1$.
 \item $g(x) = \widetilde{g}(x) + C = 2x$.
 \item $b = g(b') = 4$ and $b(y) = a(y) + (b-a) = 4-y$.
\end{itemize}
It now follows that:
\begin{equation}
\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x) := \int_{a(y)}^{b(y)} f(x)dx, 
\end{equation}
with $a(y) = 1-y$, $b(y) = 4-y$ and $C=-1$.

@@

\noindent
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_{a'}^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to equation~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_{a'}^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
% As an example if $f(t)=t$, $n=2$ and $a'=0$ then equation~\eqref{eq:cauchy} reduces to:
% \begin{equation}
% _{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
% \end{equation}
The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function $\Gamma(\alpha)$:
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Recall that $\Gamma(\alpha) := \int_0^{\infty} k^{\alpha-1} e^{-k}\,dk$. Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
% As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
% equation~\eqref{eq:frac_integral} reduces to:
% \begin{equation}
% _0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
% \end{equation}

@@

\section{Geometric Interpretation of the Left-sided Riemann-Liouville Fractional Integral}

\subsection{Converting into a Riemann-Stieltjes integral}
Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral \cite{podlubny02}:

\begin{equation}
\label{eq:rl_to_rs}
_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau), 
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
\widetilde{g}_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}
Moreover, the function $\widetilde{g}_t^{\alpha}(\tau)$ is invertible. Its inverse is:
\begin{equation}
\label{eq:h}
\widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
\end{equation}
The function $\widetilde{g}_t^{\alpha}$ is invertible, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$. Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The functions $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh} for $\alpha\in\mathsf{A}$.\\

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{gh.pdf}
\caption{This figure depicts the curves of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $\widetilde{g}$ are plotted using solid lines, while the curves plotted using dashed lines are associated with $\widetilde{h}$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.}
\label{fig:gandh}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{vis_old.pdf}
\caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
As is indicated in the figure, the graphs contained in each row of the subfigure-grid are obtained by varying $\alpha$, while the graphs contained in each column of the subfigure-grid are obtained by varying $t$. The fence in each subfigure is depicted in green. The areas depicted in red (the shadows of the fences) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.  The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively (in each subfigure). The intersection between the blue and cyan surfaces in each subfigure represents the curve that determines the height of the fence in each subfigure (it is depicted as a dashed curve).   
}
\label{fig:vis_old}
\end{figure}

\subsection{Converting into a Cavalieri integral}
\label{sec:rl_to_cav}
Recall that,
\begin{equation}
_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau). 
\end{equation}
%Furthermore, note that for all $K\in\mathbb{R}$ (see Theorem~\ref{}):
%\begin{equation}
%\int_{a'}^{t} f(\tau)~d\,[\widetilde{g}_t^{\alpha}(\tau)+K] = \int_{a'}^{t} f(\tau)~d%\,\widetilde{g}_t^{\alpha}(\tau),  
%\end{equation}
%Moreover, let $C$ be a real-valued constant so that with $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$. 
%Recall, if we wish to convert a Riemann-Stieltjes integral into a Cavalieri integral we normally first need to convert the given Riemann-Stieltjes integral into an equivalent 
%Riemann-Stieltjes integral which we can  by computing a value for $C$. This latter integral can then be converted into a Cavalieri integral. The steps that are required to perform this conversion in the case of Eq is presented below (see Section~\ref{}):
Let us first compute the following (see Section~\ref{sec:cav_integral}):
\begin{itemize}
 \item $a_t^{\alpha}(y) = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y)+ \widetilde{g}_t^{\alpha}(a')$.
 \item $a = a_t^{\alpha}(0)$.
 \item $C = a - \widetilde{g}_t^{\alpha}(a')$.
 \item $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$.
 \item $b = g_t^{\alpha}(b')$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
\end{itemize}
It now follows that:
\begin{equation}
\label{eq:rl_to_c}
_{a'}I_t^{\alpha}\,f(t) =  \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau= \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau) := \int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)\,d\tau.
\end{equation}

@@

\noindent
Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$ (see equation~\eqref{eq:h}). Interestingly, Theorem~\ref{t:conv} implies that we can use $h_t^{\alpha}(\tau)$ to convert equation~\eqref{eq:rl_to_c} into the following Riemann integral:
\begin{equation}
\label{eq:rl_to_r}
\int_{g_t^{\alpha}(a')}^{g_t^{\alpha}(t)} f\circ h_{\alpha}^t (\tau) d\tau.  
\end{equation}
We can, therefore, evaluate equation~\eqref{eq:frac_integral} in one of two ways: we can either evaluate equation~\eqref{eq:rl_to_rs} or we can evaluate equation~\eqref{eq:rl_to_r}.\\

%\subsection{Examples}
\noindent
Consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
_0I_t^{\alpha} f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{sec:rl_to_cav}):
\begin{equation}
\label{eq:ex1}
_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau):=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
\end{equation}
with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$ and $C=0$.
Note, that for this example $a'=a=0$. The non-static non-rectangular sum-based geometric interpretation associated with equation~\eqref{eq:ex1} is depicted in Figure~\ref{fig:geo1} (see Section~\ref{sec:rl_to_cav}). We elaborate further below.\\

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
\caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex1_raw}.}
\label{fig:geo1}
\end{figure}

@@

\noindent
Let $\mathsf{T}=\{2,4,6,8,10\}$ and $\mathsf{A} = \{0.2,0.4,0.6,0.8\}$. Moreover, let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
right-most edge of $R_{t}^{\alpha}$. The region $R_{t}^{\alpha}$ is not bounded by $a_{t}^{\alpha}(y)$, since $a'=a=0$. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Figure~\ref{fig:geo1}. The regions that are depicted in each of the panels of Figure~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, the larger the $t$-value is that is associated with it.\\

>>>>

\noindent
The notation $(\cdot)^{-1}$ denotes the functional inverse. The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively. Furthermore,
\begin{equation}
\label{eq:h_def}
h(x) = g^{-1}(x) 
\end{equation}
and
\begin{equation}
\label{eq:g_def}
g(x) = x - a\circ f(x) + a 
\end{equation}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{fig13.pdf}
\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$. The figure also depicts the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ as used in the Cavalieri sum (see equation~\eqref{eq:cav_sum}). Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
\label{fig:caval2}
\end{figure}

@@

\noindent
Let us express this idea more formally. Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$. Furthermore, consider the following lower Cavalieri sum (see Definition~\ref{def:cav_integral} and equation~\ref{eq:c_low}):
\begin{equation}
\label{eq:cav_sum}
\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in the left panel of Figure~\ref{fig:caval2} (for the case when $n$ is set to 3). Note that $\Delta x_i^1$ represents the width, $f(x_i^2)$ the height and $f(x_i^2)\Delta x_i^1$ the area of the $i^{\textrm{th}}$ non-rectangular integration strip depicted in Figure~\ref{fig:caval2} (due to Cavalieri's principle). Equation~\eqref{eq:cav_sum}, therefore, approximates the area of $R$. In the limit equation~\eqref{eq:cav_sum} approaches 
the Cavalieri integral (see Definition~\ref{def:cav_integral}):
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
If we evaluate the above integral we obtain the area of $R$. It is, however, quite hard to evaluate the above integral in its present form. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
integral by using the functions $h$ and $g$ (see equation~\eqref{eq:g_def} and equation~\eqref{eq:h_def}). Expressed mathematically (see Theorem~\ref{t:conv}):
\begin{equation}
\label{eq:main_cav}
\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x),
\end{equation}
We can, therefore, evaluate equation~\eqref{eq:main_cav} in one of two ways:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75,  
\end{equation}
or
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
\end{equation}
Note: $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.\\

@@

\noindent
The natural question now arises, can we convert a Riemann-Stieltjes integral into a Cavalieri integral? As an example, can $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x) = \int_{\frac{1}{2}}^2 x\,d[2x+1]$ be converted into a Cavalieri integral? Note: $f(x) = x$ and $\widetilde{g}(x) = 2x+1$. 
To accomplish this task we first need to compute the following (see Section~\ref{sec:cav_integral}):
\begin{itemize}
 \item $a(y) = f^{-1}(y) - \widetilde{g}\circ f^{-1}(y)+ \widetilde{g}(a') = 1-y$.
 \item $a = a(0) = 1$ and $C = a - \widetilde{g}(a') = -1$.
 \item $g(x) = \widetilde{g}(x) + C = 2x$.
 \item $b = g(b') = 4$ and $b(y) = a(y) + (b-a) = 4-y$.
\end{itemize}
It now follows that:
\begin{equation}
\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x) := \int_{a(y)}^{b(y)} f(x)dx, 
\end{equation}
with $a(y) = 1-y$, $b(y) = 4-y$ and $C=-1$.

@@

\noindent
If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
\begin{equation}
\label{eq:n_anti}
_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_{a'}^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
\end{equation}
Applying Cauchy's repetitive integration formula to equation~\eqref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_{a'}^t (t-\tau)^{n-1}f(\tau)~d\tau.
\end{equation}
% As an example if $f(t)=t$, $n=2$ and $a'=0$ then equation~\eqref{eq:cauchy} reduces to:
% \begin{equation}
% _{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
% \end{equation}
The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $n$ with the real value $\alpha$ and $(n-1)!$ with the Gamma function $\Gamma(\alpha)$:
\begin{equation}
\label{eq:frac_integral}
_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
\end{equation}
Recall that $\Gamma(\alpha) := \int_0^{\infty} k^{\alpha-1} e^{-k}\,dk$. Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
% As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
% equation~\eqref{eq:frac_integral} reduces to:
% \begin{equation}
% _0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}. 
% \end{equation}

@@

\section{Converting into a Riemann-Stieltjes integral}
Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral \cite{podlubny02}:

\begin{equation}
\label{eq:rl_to_rs}
_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau), 
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
\widetilde{g}_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}
Moreover, the function $\widetilde{g}_t^{\alpha}(\tau)$ is invertible. Its inverse is:
\begin{equation}
\label{eq:h}
\widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
\end{equation}
The function $\widetilde{g}_t^{\alpha}$ is invertible, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$. Let $\mathsf{A} = \{0.2,0.4,0.6,0.8\}$. The functions $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh} for $\alpha\in\mathsf{A}\cup\{0,1\}$.\\

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{gh.pdf}
\caption{This figure depicts the curves of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}\cup\{0,1\}$. The curves associated with $\widetilde{g}$ are plotted using solid lines, while the curves plotted using dashed lines are associated with $\widetilde{h}$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.}
\label{fig:gandh}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{vis_old.pdf}
\caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
As is indicated in the figure, the graphs contained in each row of the subfigure-grid are obtained by varying $\alpha$, while the graphs contained in each column of the subfigure-grid are obtained by varying $t$. The fence in each subfigure is depicted in green. The areas depicted in red (the shadows of the fences) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.  The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively (in each subfigure). The intersection between the blue and cyan surfaces in each subfigure represents the curve that determines the height of the fence in each subfigure (it is depicted as a dashed curve).   
}
\label{fig:vis_old}
\end{figure}

\section{Converting into a Cavalieri integral}
\label{sec:rl_to_cav}
Recall that:
\begin{equation}
_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau). 
\end{equation}
%Furthermore, note that for all $K\in\mathbb{R}$ (see Theorem~\ref{}):
%\begin{equation}
%\int_{a'}^{t} f(\tau)~d\,[\widetilde{g}_t^{\alpha}(\tau)+K] = \int_{a'}^{t} f(\tau)~d%\,\widetilde{g}_t^{\alpha}(\tau),  
%\end{equation}
%Moreover, let $C$ be a real-valued constant so that with $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$. 
%Recall, if we wish to convert a Riemann-Stieltjes integral into a Cavalieri integral we normally first need to convert the given Riemann-Stieltjes integral into an equivalent 
%Riemann-Stieltjes integral which we can  by computing a value for $C$. This latter integral can then be converted into a Cavalieri integral. The steps that are required to perform this conversion in the case of Eq is presented below (see Section~\ref{}):
Let us first compute the following (see Section~\ref{sec:cav_integral}):
\begin{itemize}
 \item $a_t^{\alpha}(y) = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y)+ \widetilde{g}_t^{\alpha}(a')$.
 \item $a = a_t^{\alpha}(0)$.
 \item $C = a - \widetilde{g}_t^{\alpha}(a')$.
 \item $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$.
 \item $b = g_t^{\alpha}(t)$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
\end{itemize}
It now follows that:
\begin{equation}
\label{eq:rl_to_c}
_{a'}I_t^{\alpha}\,f(t) =  \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau= \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau) := \int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)\,d\tau.
\end{equation}

@@

\noindent
Let $h_t^{\alpha}(\tau)$ be equal to the functional inverse of $g_t^{\alpha}(\tau)$ (see equation~\eqref{eq:h}). Interestingly, Theorem~\ref{t:conv} implies that we can use $h_t^{\alpha}(\tau)$ to convert equation~\eqref{eq:rl_to_c} into the following Riemann integral:
\begin{equation}
\label{eq:rl_to_r}
\int_{g_t^{\alpha}(a')}^{g_t^{\alpha}(t)} f\circ h_{\alpha}^t (\tau) d\tau.  
\end{equation}
We can, therefore, evaluate equation~\eqref{eq:frac_integral} in one of two ways: we can either evaluate equation~\eqref{eq:rl_to_rs} or we can evaluate equation~\eqref{eq:rl_to_r}.

\section{Examples}
\noindent
Consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
_0I_t^{\alpha} f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{sec:rl_to_cav}):
\begin{equation}
\label{eq:ex1}
_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau):=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
\end{equation}
with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$ and $C=0$.
Note, that for this example $a'=a=0$. The non-static non-rectangular sum-based geometric interpretation associated with equation~\eqref{eq:ex1} is depicted in Figure~\ref{fig:geo1} (see Section~\ref{sec:rl_to_cav}). We elaborate further below.\\

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{geo_int1.pdf}
\caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex1_raw}.}
\label{fig:geo1}
\end{figure}

@@

\noindent
Let $\mathsf{T}=\{2,4,6,8,10\}$ and $\mathsf{A} = \{0.2,0.4,0.6,0.8\}$. Moreover, let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
right-most edge of $R_{t}^{\alpha}$. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Figure~\ref{fig:geo1}. The regions that are depicted in each of the panels of Figure~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, the larger the $t$-value is that is associated with it.\\
